---
title: "Div I Project"
author: "Jacqueline Chen"
date: "October 9, 2019"
output: 
  html_document:
    toc: yes
    toc_float: yes
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Metadata

### Purpose

What is the purpose of your function? What problem does it solve? When would you use it? 

My function works to get all the possible combinations for drawing a specified number of elements in a given list, where order doesn't matter. It helps solve problems related to organization or probability. I would use it when figuring out how many different teams of 3 people can we pick from a total group of 15 or what is the probability that a 4 digit password has no repeated digits. 

### Dependencies/Setup

> Load any packages or other pre-processing steps that are necessary to make your function work in the chunk below. The chunk should be as [parsimonious](https://en.wiktionary.org/wiki/parsimonious) as possible.
```{r load, message=FALSE}
library(tidyverse)
```


### Arguments

List the arguments your function takes. Specify the data type, default value (if applicable), and any other assumptions you are making about the value of each argument.

- `x`: a list of numeric or character vectors
- `r``: a numeric vector

### Result

What does your function return? Specify the data type and any other assumptions you are making. 

-It returns a numeric vector which represents the number of all the possible combinations of elements from the list `x` and it also returns characters where each of them represents a plausible combination. 

## Code

Paste your code in the chunk below. 
```{r code}
combination <- function(x, r) {
  n = length(x)
  
  #The number of possible combinations of r elements in list x: 
  nCr = factorial(n)/(factorial(r)*factorial(n-r))
  print(nCr)
  
  #Print all possible combinations: 
  h = 0
  g = 1

  while (h < n-r+2) { 
  h = h + 1
  e = h
  g = h + 1
  
    while (e < n-r+2){
      e = e + 1 
      a = paste(x[h], x[e], sep="")
      
      while (nchar(a) < r){ 
        g = g + 1
        a = paste(a, x[g], sep="")}
        print(a)

      if ( r > 2) {
        f = g + 1
      if ( h < n-1 ){
          if ( f == n) {
            print(paste(str_sub(a, 1, -2), x[f], sep=""))}
    
          if ( f < n) {
            for (k in seq(f,n)){
            print(paste(str_sub(a, 1, -2), x[k], sep=""))
            }}}
        }}}
}
```

## Examples

> Give 2-3 examples of typical usage of your function. Describe in words what is being illustrated.

This shows the number of possible arrangements by selecting 3 elements from a list of length 6 with no repetition; then it prints out all the 20 possible arrangements. 

```{r ex1}
# First Example 
x = c("a", "b", "c", "d", "e", "f")
y = combination(x, 3)
```

This shows the number of possible arrangements by selecting 3 elements from a list of length 4 with no repetition; then it prints out all the 4 possible arrangements. 

```{r ex2}
#Second Example 
x = c(1,2,3,4)
combination(x, 3)
```

## Testing

Provide a few examples of outputs that you expect your function will match, given a specific input. [Best if you use the [`testthat` package](https://github.com/r-lib/testthat).] 

```{r tests, message=FALSE}
# I would expect the output of combination(c(1,2,3), 2) to be: 3, 12, 13, 23
combination(c(1,2,3), 2)

# I would expect the output of combination(c("c","a","b","d","e" ), 2) to be: 10, cab, cad, cae, cbd, cbe, cde, abd, abe, ade, bde, 
combination(c("c","a","b","d","e") , 3) 

```